Optimizing Abstract$^{\text 2}$ Machines

### 2012-11-08 paper/paper.tex
Resolve conflicts in paper.

\documentclass[preprint]{sigplanconf}
\usepackage{alltt}
\usepackage{amsmath,amsthm}
\usepackage{amssymb}
\usepackage{stmaryrd}

@@

\begin{abstract}
Recently \emph{abstracting abstract machines} has been proposed as a
systematic approach to designing sound and computable program analyses
for higher-order programming languages.  The approach has been applied
to a wide variety of languages with features widely considered
difficult to analyze

The abstracting abstract machines approach to program analysis makes
it easy to design and implement sound and computable abstract
interpretations of higher-order programs.
%
However, the straightforward implementation is generally
not very fast.
%
This article contributes a step by step process for going from a naive
abstract$^2$ machine to an efficient program analyzer that is (nearly)
three orders of magnitude faster than the starting point, yet just as
precise (and purely functional).
\end{abstract}

@@

@@

\bibliographystyle{splncs}
\bibliography{bibliography}

>>>>

\documentclass[preprint,onecolumn,9pt]{onecol} %{sigplanconf}
\usepackage{alltt}
\usepackage{amsmath,amsthm}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{url}

@@

\begin{abstract}
Abstracting abstract machines has recently been proposed as a
lightweight approach to designing sound and computable program
analyses.  The approach involves deriving abstract interpreters from
existing machine semantics and has been applied to a variety of
languages with features widely considered difficult to analyze.
Although analyzers are straightforward to build under this approach,
the resulting analyzer is prohibitively inefficient.

This article contributes a step by step process for going from a naive
analyzer derived under the abstracting abstract machine approach, to
an efficient program analyzer.
\end{abstract}

@@

The \emph{abstracting abstract machines}
approach~\cite{dvanhorn:VanHorn2011Abstracting,dvanhorn:VanHorn2012Systematic}
to deriving program analyses provides a straightforward way of
transforming a programming language semantics in the form of an
abstract machine, into a family of abstract interpreters parameterized
over policies for regulating the analytic precision of the control,
environment, store, and base value domains.  By taking a
machine-oriented view of computation, it becomes possible to design,
verify, and implement program analyzers for realistic language
features typically considered difficult to model.  The approach was
originally applied to features such as higher-order functions,
stack-inspection, exceptions, laziness, first-class continuations, and
garbage collection.  It has since been used to verify actor-based
parallelism~\cite{local:DOsualdo:12A} and behavioral
contracts~\cite{FIXME:tobin-hochstadt}; it has been used to model
Dalvik, Erlang~\cite{local:DOsualdo:12B},
JavaScript~\cite{local:DBLP:journals/corr/abs-1109-4467}, Racket, and
Coq~\cite{local:harvard}.

The primary strength of the approach is that abstract interpreters can
be easily derived through a small number of steps from existing
machine models.% such as the CESK machine or the Lazy Krivine machine.
Moreover, since the relationships between abstract machines and
higher-level semantic models---such as definitional
interpreters~\cite{dvanhorn:reynolds-hosc98}, structured operational
semantics~\cite{dvanhorn:Plotkin1981Structural}, and reduction
semantics~\cite{dvanhorn:Felleisen2009Semantics}---are well
understood~\cite{dvanhorn:Danvy:DSc}, it is possible to navigate from
these semantic models to sound program analyzers.

%% Using this approach has also lead to new insights in pushdown
%% abstractions of programs capable of precisely modeling the program
%% stack, even in the presence of control effects.

@@

\bibliographystyle{plain}
\bibliography{local,bibliography}
